Redundant calibration as a complex optimization problem

### 2017-01-12 paper.tex
added conclusion

\section{Redundant Calibration}
As discussed in Section~\ref{sec:ls}, we can solve Eq.~\eqref{eq:least_squares_red} in one of two ways. We can split the problem into its real and
imaginary parts and then solve for the real and imaginary parts of the parameters seperately or we can employ the notion of Wirtinger derivatives. The former 
approach is discussed in Section~\ref{sec:ri}, while the latter approach is described in detail in Section~\ref{sec:w}.

@@

\subsubsection{Complex GN and LM}
In this section we discuss how we can use the GN and LM algorithms to solve Eq.~\eqref{eq:least_squares_complex} (i.e. estimate $\breve{\bz}$). The complex Jacobian is defined to be
\begin{equation}
\label{eq:Jacobian}
\bJ = \begin{bmatrix}
       \bmJ & \bmJ^*\\
       \conj{\bmJ}^* & \conj{\bmJ} 
      \end{bmatrix},
\end{equation}
where 
\begin{align}
\bmJ &= \frac{\partial \bv}{\partial \bz}, & \bmJ^* &= \frac{\partial \bv}{\partial \conj{\bz}}. 
\end{align}
In Eq.~\eqref{eq:Jacobian}, $\frac{\partial}{\partial \bz}$ and $\frac{\partial}{\partial \conj{\bz}}$ respectively denote the cogradient operator and the conjugate cogradient operator \citep{Sorber2012}.
The GN update step is now defined as:
\begin{equation}
\label{eq:GN_update}
 \Delta \breve{\bz} = (\bJ^H\bJ)^{-1}\bJ^H\breve{\br}.
\end{equation}
The LM update rule is very similar, the major difference being a damping factor $\lambda$ is introduced:
\begin{equation}
\label{eq:LM_update}
\Delta \breve{\bz} = (\bJ^H\bJ + \lambda\bD)^{-1}\bJ^H\breve{\br},
\end{equation}
where $\bD=\bI\odot\bJ^H\bJ$. We refer to $\bJ^H\bJ$ as the Hessian matrix $\bH$ and to $\bJ^H\bJ + \lambda\bD$ as the modified Hessian matrix $\bmH$.

@@

\section{Conclusion}
In Section~\ref{sec:} we showed that instead of using the traditional phase-and-amplitude approach to perform redundant calibration we can actually use a purely complex
framework. In this framework the unknown variables and their conjugates are treated as independent variables that have to be estimated. We have also 
proposed to use the LM algorithm, instead of the GN algorithm, to perform the actual parameter estimation within this complex framework. The LM algorithm exhibits better convergence properties than the 
GN algorithm. This has the immediate consequence that the amount of algorithmic layers that are needed to perform redundant calibration are reduced.
Them most expensive operation associated with the LM algorithm (as well as the GN algorithm) is the inversion of $\bH$.
We also compared the computational complexity of two previously proposed algorithms to efficiently invert $\bH$ for the redundant calibration use case, namely 
ADI and PCG. We showed that the computational complexity of the ADI method is $\mathbb{O}(P)$, while the computational complexity of the PCG method is asymptotically bounded
by $\mathbb{O}(P^2)$. Both of these algorithms perform much better than stock standard inversion, which has a computational complexity of $\mathbb{O}(P^3)$.
Although the ADI method does execute faster than the PCG method it is far less robust as it would be less straightforward to apply to other calibration uses cases. The reason being,
the diagonal approximation we make with might not be accurate

>>>>

\section{Redundant Calibration}
\label{sec:main_sec}
As discussed in Section~\ref{sec:ls}, we can solve Eq.~\eqref{eq:least_squares_red} in one of two ways. We can split the problem into its real and
imaginary parts and then solve for the real and imaginary parts of the parameters seperately or we can employ the notion of Wirtinger derivatives. The former 
approach is discussed in Section~\ref{sec:ri}, while the latter approach is described in detail in Section~\ref{sec:w}.

@@

\subsubsection{Complex GN and LM}
\label{sec:complex_GN_LM}
In this section we discuss how we can use the GN and LM algorithms to solve Eq.~\eqref{eq:least_squares_complex} (i.e. estimate $\breve{\bz}$). The complex Jacobian is defined to be
\begin{equation}
\label{eq:Jacobian}
\bJ = \begin{bmatrix}
       \bmJ & \bmJ^*\\
       \conj{\bmJ}^* & \conj{\bmJ} 
      \end{bmatrix},
\end{equation}
where 
\begin{align}
\bmJ &= \frac{\partial \bv}{\partial \bz}, & \bmJ^* &= \frac{\partial \bv}{\partial \conj{\bz}}. 
\end{align}
In Eq.~\eqref{eq:Jacobian}, $\frac{\partial}{\partial \bz}$ and $\frac{\partial}{\partial \conj{\bz}}$ respectively denote the cogradient operator and the conjugate cogradient operator \citep{Sorber2012}.
The GN update step is now defined as:
\begin{equation}
\label{eq:GN_update}
 \Delta \breve{\bz} = (\bJ^H\bJ)^{-1}\bJ^H\breve{\br}.
\end{equation}
The LM update rule is very similar, the major difference being a damping factor $\lambda$ is introduced:
\begin{equation}
\label{eq:LM_update}
\Delta \breve{\bz} = (\bJ^H\bJ + \lambda\bD)^{-1}\bJ^H\breve{\br},
\end{equation}
where $\bD=\bI\odot\bJ^H\bJ$. We refer to $\bJ^H\bJ$ as the Hessian matrix $\bH$ and to $\bJ^H\bJ + \lambda\bD$ as the modified Hessian matrix $\bmH$.

@@

\section{Conclusion}
In Section~\ref{sec:main_sec} we showed that instead of using the traditional phase-and-amplitude approach to perform redundant calibration we can actually use a purely complex
framework. In this framework the unknown variables and their conjugates are treated as independent variables that have to be estimated. 
We then derived the GN and LM update steps associated with this complex framework (see Section~\ref{sec:complex_GN_LM}). In this paper we focused more on the LM algorithm than on the GN algorithm. The LM algorithm exhibits better convergence properties than the 
GN algorithm. This has the immediate consequence that the amount of algorithmic layers that are needed to perform redundant calibration are reduced.

The most expensive operation associated with the LM algorithm (as well as the GN algorithm) is the inversion of $\bH$.
We compared the computational complexity of two previously proposed algorithms to efficiently invert $\bH$ for the redundant calibration use case in Section~\ref{sec:results}, namely 
ADI \citep{Marthi2014} and PCG \citep{Liu2010}. We showed that the computational complexity of the ADI method is $\mathbb{O}(P)$, while the computational complexity of the PCG method is asymptotically bounded
by $\mathbb{O}(P^2)$. Both of these algorithms perform much better than stock standard inversion, which has a computational complexity of $\mathbb{O}(P^3)$.
Although the ADI method does execute faster than the PCG method it is far less robust as it would be less straightforward to apply to other calibration uses cases. The reason being,
the diagonal approximation we make with ADI might not be accurate enough in general.

Lastly, we showed how \citet{Marthi2014}, \citet{Salvini2014} and \citet{Smirnov2015} relate to each other (see Section~\ref{sec:red_c}). The ADI method associated with skymodel-based calibration (i.e. \textsc{StEfCal}) is presented
in \citet{Salvini2014}. \citet{Smirnov2015} showed that it is possible to rederive this skymodel-based ADI method through complex optimization. In particular, they showed that if 
we approximate the $\bH$ associated with the LM algorithm with its diagonal then we can rederive the ADI update rules presented in \citet{Salvini2014}. 
\citet{Marthi2014} applied the ADI method to the redundant use case. This fact is not immediatly clear when inspecting \citet{Marthi2014}. The ADI update rules presented \citet{Marthi2014} were derived by taking the partial derivatives of 
the objective function towards the unknown parameters, setting the intermediate results to zero and then solving for the unknowns. In this paper we show that 
these same ADI update rules can be derived using the diagonal approximation technique proposed in \citet{Smirnov2015}. The fact that we can use this diagonal approximation
technique to derive these update rules imply that the algorithm presented in \citet{Marthi2014} is in fact the ADI method (i.e. redundant \textsc{StEfCal}). This same
fact can be established by directly applying the skymodel-based ADI derivation presented in \citet{Salvini2014} to the redundant use case.
